\sysfull

### 2017-08-04 paper/systemdescription.tex
VIPER block diagram placeholder add
placeholder for VIPER API figure
change or order of contributions in system description
added placeholdef for viper syntax in ststem description

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{\sys top-level view.}
	\label{fig:system_overview}
\end{figure}

@@

\begin{itemize}
	\item \textbf{Task coalescing}: details will be provided in Section~\ref{sec:task_coalescing}
	\item \textbf{Memory virtualization}: details will be provided in Section~\ref{sec:memory_virtulaization}
	\item \textbf{Compiler support}: details will be provided in Section~\ref{sec:compiler}
\end{itemize}

@@

@@

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/viper_block_diagram}
	\caption{\sys top-level view.}
	\label{fig:system_overview}
\end{figure}

@@

\begin{itemize}
	\item \textbf{Compiler-supported automatic task generator}: details will be provided in Section~\ref{sec:compiler}
	\item \textbf{Memory virtualization}: details will be provided in Section~\ref{sec:memory_virtulaization}
	\item \textbf{Task coalescing}: details will be provided in Section~\ref{sec:task_coalescing}
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/taskification_example}
	\caption{\sys API.}
	\label{fig:system_overview}
\end{figure}

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\texttt{\_\_task\_\_ foo(){...}} & Task declaration\\
		\texttt{addTask()} & Build internal data structure for executor \\
		\texttt{run\_tasks()} & Task executor \\ %scheduler
		\texttt{next\_task()} & Transition to a new task\\
		%\texttt{PageFault()} & --- \\
		%\texttt{P()} & ---\\
		\hline
	\end{tabular}
\caption{Summary of \sys syntax: top---user-specific variables}
\label{tab:viper_syntax}
\end{table}
